An Automatic Verification Framework for Software Configurations

### 2016-05-10 OSDI/learner.tex
lala

\para{Our approach.}
In \app's learner module, the rule learning mechanism is tolerant 
enough to accept a dataset {\em full of} incorrect configuration files. 
Rather than manually correcting each file, 
we extend the previous formalism to run probabilistic learning
on our intermediate representations (generated by the translator).

>>>>

\para{Our approach.}
In \app's learner module, the rule learning mechanism is tolerant 
enough to accept a dataset of possibly incorrect configuration files. 
Rather than manually correcting each file, 
we extend the previous formalism to run probabilistic learning
on our intermediate representations (generated by the translator).
